---
title: "Data Graphs"
author: "James Matheson"
date: "July 19, 2018"
output:
  html_document: default
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(GGally)
library(gridExtra)
results_train <- read_csv("results_train.csv")
```

```{r correlation chart, echo=FALSE}
ggcorr(results_train[, ], nbreaks = 4, palette = "RdGy", label = TRUE, label_size = 3, label_color = "white")
```


##Loan Type and Loan Type v. Target

```{r loan_type, echo=FALSE}
grid.arrange(ggplot(results_train, aes(x = LOAN_TYPE, fill = LOAN_TYPE)) +
               geom_bar(stat = "count"),
             ggplot(results_train, aes(LOAN_TYPE, TARGET, fill = LOAN_TYPE)) +
               geom_bar(position = "dodge", stat = "summary", fun.y = "mean")
             )
count(results_train, LOAN_TYPE)
```

## Age and Age v. Target

```{r age, echo=FALSE}
grid.arrange(ggplot(results_train, aes(x = AGE)) +
               geom_histogram(stat = "bin", bins = 20, col = "grey", fill = "blue"),
             ggplot(results_train, aes(factor(TARGET), AGE, fill = AGE)) +
               geom_jitter( alpha = .05)  +
               geom_boxplot( alpha = .5, color = "blue") +
               stat_summary(fun.y = "mean", geom = "point", color = "red", shape = 8, size = 4)
             )
summary(results_train$AGE)
```

## Gender and Gender v. Target

```{r gender, echo=FALSE}
grid.arrange(ggplot(results_train, aes(x = GENDER, fill = GENDER)) +
               geom_bar(stat = "count"),
             ggplot(results_train, aes(GENDER, TARGET, fill = GENDER)) +
               geom_bar(position = "dodge", stat = "summary", fun.y = "mean")
             )
count(results_train, GENDER)
```

## Owns a car? and Owns Car v. Target

```{r owns_car, echo=FALSE}
grid.arrange(ggplot(results_train, aes(x = OWNS_CAR, fill = OWNS_CAR)) +
               geom_bar(stat = "count"),
             ggplot(results_train, aes(OWNS_CAR, TARGET, fill = OWNS_CAR)) +
               geom_bar(position = "dodge", stat = "summary", fun.y = "mean")
             )
count(results_train, OWNS_CAR)
```

## Age of car and Age of Car v. Target

```{r age_of_car, echo=FALSE}
grid.arrange(ggplot(results_train, aes(x = AGE_OF_CAR)) +
               geom_histogram(stat = "bin", binwidth = 2.5, col = "grey", fill = "blue"),
             ggplot(results_train, aes(factor(TARGET), AGE_OF_CAR)) +
               geom_jitter( alpha = .05)  +
               geom_boxplot( alpha = .5, color = "blue") +
               stat_summary(fun.y = "mean", geom = "point", color = "red", shape = 8, size = 4)
)
summary(results_train$AGE_OF_CAR)
count(results_train, factor(AGE_OF_CAR))
```
##NEED TO FIX OUTLIERS AND DETERMINE THE CAUSE OF THE BLIP AROUND 62

## Owns Real Estate? and Owns RE v. Target

```{r owns_realty, echo=FALSE}
grid.arrange(ggplot(results_train, aes(x = OWNS_REALTY, fill = OWNS_REALTY)) +
               geom_bar(stat = "count"),
             ggplot(results_train, aes(OWNS_REALTY, TARGET, fill = OWNS_REALTY)) +
               geom_bar(position = "dodge", stat = "summary", fun.y = "mean")
             )
count(results_train, OWNS_REALTY)
```

## Number of Children and Number of Children v. Target

```{r children, echo=FALSE}
grid.arrange(ggplot(results_train, aes(x = factor(CHILDREN), fill = CHILDREN)) +
               geom_bar(stat = "count"),
             ggplot(results_train, aes(factor(CHILDREN), TARGET, fill = CHILDREN)) +
               geom_bar(position = "dodge", stat = "summary", fun.y = "mean")
             )
count(results_train, CHILDREN)
```

## Total Income and Total Income v. Target

```{r total_income, echo=FALSE}
grid.arrange(ggplot(results_train, aes(x = TOTAL_INCOME)) +
  geom_histogram(bins = 20, col = "grey", fill = "blue") +
    xlim(0, 500000),
  # scale_y_log10()
  ggplot(results_train, aes(factor(TARGET), TOTAL_INCOME)) +
               geom_jitter( alpha = .05)  +
               geom_boxplot( alpha = .5, color = "blue") +
               stat_summary(fun.y = "mean", geom = "point", color = "red", shape = 8, size = 4) +
    ylim(0, 500000)
)
summary(results_train$TOTAL_INCOME)
```

<!-- ## Total Income and Total Income v. Target -->

<!-- ```{r echo=FALSE} -->
<!-- ggplot(results_train, aes(x = TOTAL_INCOME)) + -->
<!--   geom_histogram(bins = 20) + -->
<!--   scale_x_log10(breaks=c(1e+5,1e+6)) + -->
<!--   xlim(0, 1e+6) -->
<!-- summary(results_train$TOTAL_INCOME) -->
<!-- ``` -->

## Amount of Loan and Amount of Loan v. Target

```{r loan_amount, echo=FALSE}
grid.arrange(ggplot(results_train, aes(x = LOAN_AMOUNT)) +
  geom_histogram(stat = "bin", bins = 20, col = "grey", fill = "blue"),
  ggplot(results_train, aes(factor(TARGET), LOAN_AMOUNT)) +
               geom_jitter( alpha = .05)  +
               geom_boxplot( alpha = .5, color = "blue") +
               stat_summary(fun.y = "mean", geom = "point", color = "red", shape = 8, size = 4)
)
summary(results_train$LOAN_AMOUNT)
```

## Monthly Payment and Monthly Payment v. Target

```{r annuity_amount, echo=FALSE}
grid.arrange(ggplot(results_train, aes(x =  ANNUITY_AMOUNT)) +
               geom_histogram(stat = "bin", col = "grey", fill = "blue") +
               xlim(0, 1e+5),
             ggplot(results_train, aes(factor(TARGET), ANNUITY_AMOUNT)) +
               ylim(0, 1e+5) +
               geom_jitter( alpha = .05)  +
               geom_boxplot( alpha = .5, color = "blue") +
               stat_summary(fun.y = "mean", geom = "point", color = "red", shape = 8, size = 4)
)
  
summary(results_train$ANNUITY_AMOUNT)
```

## Price of Goods Purchcased with the Loan and Price v. Target

```{r purchase_price_of_goods, echo=FALSE}
grid.arrange(ggplot(results_train, aes(x = PURCHASE_PRICE_OF_GOODS)) +
               geom_histogram(stat = "bin", col = "grey", fill = "blue"),
             ggplot(results_train, aes(factor(TARGET), PURCHASE_PRICE_OF_GOODS)) +
               geom_jitter( alpha = .05)  +
               geom_boxplot( alpha = .5, color = "blue") +
               stat_summary(fun.y = "mean", geom = "point", color = "red", shape = 8, size = 4)
)
summary(results_train$PURCHASE_PRICE_OF_GOODS)
```

## Ratio of Loan to Payment Amount and Ratio v. Target

```{r ratio_loan_to_annuity, echo=FALSE}
grid.arrange(ggplot(results_train, aes(x = RATIO_LOAN_TO_ANNUITY)) +
               geom_histogram(col = "grey", fill = "blue"),
             ggplot(results_train, aes(factor(TARGET), RATIO_LOAN_TO_ANNUITY)) +
               geom_jitter( alpha = .05)  +
               geom_boxplot( alpha = .5, color = "blue") +
               stat_summary(fun.y = "mean", geom = "point", color = "red", shape = 8, size = 4)
)
summary(results_train$RATIO_LOAN_TO_ANNUITY)
```

## Type of Income and Type of Income v. Target

```{r income_type, echo=FALSE}
grid.arrange(ggplot(results_train, aes(x = INCOME_TYPE, fill = INCOME_TYPE)) +
  geom_bar(stat = "count", show.legend = FALSE) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)),
  ggplot(results_train, aes(INCOME_TYPE, TARGET, fill = INCOME_TYPE)) +
    geom_bar(position = "dodge", stat = "summary", fun.y = "mean", show.legend = FALSE) +
    theme(axis.text.x = element_text(angle = 90))
  )
count(results_train, INCOME_TYPE)
```

## Education Level and Education Level v. Target

```{r education, echo=FALSE}
grid.arrange(ggplot(results_train, aes(x = EDUCATION, fill = EDUCATION)) +
               geom_bar(stat = "count") +
               theme(axis.text.x = element_text(angle = 90, hjust = 1)),
             ggplot(results_train, aes(EDUCATION, TARGET, fill = EDUCATION)) +
               geom_bar(position = "dodge", stat = "summary", fun.y = "mean") +
               theme(axis.text.x = element_text(angle = 90, hjust = 1))
      )
count(results_train, EDUCATION)
```

## Marital Status and Marital Status v. Target

```{r marital_status, echo=FALSE}
grid.arrange(ggplot(results_train, aes(x = MARITAL_STATUS, fill = MARITAL_STATUS)) +
               geom_bar(stat = "count"),
             ggplot(results_train, aes(MARITAL_STATUS, TARGET, fill = MARITAL_STATUS)) +
               geom_bar(position = "dodge", stat = "summary", fun.y = "mean")
)
count(results_train, MARITAL_STATUS)
```

## Housing Status and Housing Status v. Target

```{r housing_status, echo=FALSE}
grid.arrange(ggplot(results_train, aes(x = HOUSING_STATUS, fill = HOUSING_STATUS)) +
               geom_bar(stat = "count") +
               theme(axis.text.x = element_text(angle = 90, hjust = 1)),
             ggplot(results_train, aes(HOUSING_STATUS, TARGET, fill = HOUSING_STATUS)) +
               geom_bar(position = "dodge", stat = "summary", fun.y = "mean") +
               theme(axis.text.x = element_text(angle = 90, hjust = 1))
)
count(results_train, HOUSING_STATUS)
```

## Years at Current Job and Years v. Target

```{r years_at_curernt_job, echo=FALSE}
grid.arrange(ggplot(results_train, aes(x = YEARS_AT_CURRENT_JOB)) +
  geom_histogram(binwidth = 2, col = "grey", fill = "blue") +
  xlim(0, 50),
  ggplot(results_train, aes(factor(TARGET), YEARS_AT_CURRENT_JOB)) +
    ylim(0, 50) +
               geom_jitter( alpha = .05)  +
               geom_boxplot( alpha = .5, color = "blue") +
               stat_summary(fun.y = "mean", geom = "point", color = "red", shape = 8, size = 4)
)
summary(results_train$YEARS_AT_CURRENT_JOB)
```

## Employer Organization Type and Type v. Target

```{r employer_type, echo=FALSE}
grid.arrange(ggplot(results_train, aes(x = EMPLOYER_TYPE, fill = EMPLOYER_TYPE)) +
  geom_bar(stat = "count", show.legend = FALSE) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)),
  ggplot(results_train, aes(EMPLOYER_TYPE, TARGET, fill = EMPLOYER_TYPE)) +
    geom_bar(position = "dodge", stat = "summary", fun.y = "mean", show.legend = FALSE) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
)
count(results_train, EMPLOYER_TYPE)
```

## Years Since Getting Current Identity Documnent and Years v. Target

```{r years_since_doc, echo=FALSE}
grid.arrange(ggplot(results_train, aes(x = YEARS_SINCE_GETTING_IDENTITY_DOCUMENT)) +
               geom_histogram(col = "grey", fill = "blue"),
             ggplot(results_train, aes(factor(TARGET), YEARS_SINCE_GETTING_IDENTITY_DOCUMENT)) +
               geom_jitter( alpha = .05)  +
               geom_boxplot( alpha = .5, color = "blue") +
               stat_summary(fun.y = "mean", geom = "point", color = "red", shape = 8, size = 4)
)
summary(results_train$YEARS_SINCE_GETTING_IDENTITY_DOCUMENT)
```

## Rating of Region and Rating v. Target

```{r region_city_rating, echo=FALSE}
grid.arrange(ggplot(results_train, aes(x = REGION_AND_CITY_RATING, fill = factor(REGION_AND_CITY_RATING))) +
  geom_bar(stat = "count"),
  ggplot(results_train, aes(factor(REGION_AND_CITY_RATING), TARGET, fill = factor(REGION_AND_CITY_RATING))) +
    geom_bar(position = "dodge", stat = "summary", fun.y = "mean")
  )
count(results_train, REGION_AND_CITY_RATING)
```



<!-- ## Target -->

<!-- ```{r echo=FALSE} -->
<!-- ggplot(results_train, aes(x = factor(TARGET))) + -->
<!--   geom_bar(stat = "count") -->
<!-- ``` -->


<!-- ## Loan Type -->

<!-- ```{r echo=FALSE} -->
<!-- ggplot(results_train, aes(x = LOAN_TYPE )) + -->
<!--   geom_bar(stat = "count") -->
<!-- ``` -->


<!-- ## Age -->

<!-- # ```{r echo=FALSE} -->
<!-- # ggplot(results_train, aes(x = AGE)) + -->
<!-- #   geom_histogram(stat = "bin", bins = 20) -->
<!-- # ``` -->

<!-- ## Gender -->

<!-- ```{r echo=FALSE} -->
<!-- ggplot(results_train, aes(x = GENDER)) + -->
<!--   geom_bar(stat = "count") -->
<!-- ``` -->

<!-- ## Owns a car? -->

<!-- ```{r echo=FALSE} -->
<!-- ggplot(results_train, aes(x = OWNS_CAR)) + -->
<!--   geom_bar(stat = "count") -->
<!-- ``` -->

<!-- ## Age of car -->

<!-- ```{r echo=FALSE} -->
<!-- ggplot(results_train, aes(x = AGE_OF_CAR)) + -->
<!--   geom_histogram(stat = "bin", binwidth = 2.5) -->
<!-- ``` -->

<!-- ## Owns Real Estate? -->

<!-- ```{r echo=FALSE} -->
<!-- ggplot(results_train, aes(x = OWNS_REALTY)) + -->
<!--   geom_bar(stat = "count") -->
<!-- ``` -->

<!-- ## Number of Children -->

<!-- ```{r echo=FALSE} -->
<!-- ggplot(results_train, aes(x = factor(CHILDREN))) + -->
<!--   geom_bar(stat = "count") -->
<!-- ``` -->

<!-- ## Total Income -->

<!-- ```{r echo=FALSE} -->
<!-- ggplot(results_train, aes(x = TOTAL_INCOME)) + -->
<!--   geom_histogram(bins = 20) + -->
<!--   scale_x_log10(breaks=c(1e+5,1e+6)) + -->
<!--   xlim(0, 1e+6) -->
<!-- ``` -->

<!-- ## Amount of Loan -->

<!-- ```{r echo=FALSE} -->
<!-- ggplot(results_train, aes(x = LOAN_AMOUNT)) + -->
<!--   geom_histogram(stat = "bin") -->
<!-- summary(results_train$LOAN_AMOUNT) -->
<!-- ``` -->

<!-- ## Monthly Payment -->

<!-- ```{r echo=FALSE} -->
<!-- ggplot(results_train, aes(x =  ANNUITY_AMOUNT)) + -->
<!--   geom_histogram(stat = "bin") -->
<!-- ``` -->

<!-- ## Price of Goods Purchcased with the Loan -->

<!-- ```{r echo=FALSE} -->
<!-- ggplot(results_train, aes(x = PURCHASE_PRICE_OF_GOODS)) + -->
<!--   geom_histogram(stat = "bin") -->
<!-- ``` -->

<!-- ## Ratio of Loan to Payment Amount -->

<!-- ```{r echo=FALSE} -->
<!-- ggplot(results_train, aes(x = RATIO_LOAN_TO_ANNUITY)) + -->
<!--   geom_histogram() -->
<!-- ``` -->

<!-- ## Type of Income -->

<!-- ```{r echo=FALSE} -->
<!-- ggplot(results_train, aes(x = INCOME_TYPE)) + -->
<!--   geom_bar(stat = "count") + -->
<!-- theme(axis.text.x = element_text(angle = 90, hjust = 1)) -->
<!-- ``` -->

<!-- ## Education Level -->

<!-- ```{r echo=FALSE} -->
<!-- ggplot(results_train, aes(x = EDUCATION)) + -->
<!--   geom_bar(stat = "count") -->
<!-- ``` -->

<!-- ## Marital Status -->

<!-- ```{r echo=FALSE} -->
<!-- ggplot(results_train, aes(x = MARITAL_STATUS)) + -->
<!--   geom_bar(stat = "count") -->
<!-- ``` -->

<!-- ## Housing Status -->

<!-- ```{r echo=FALSE} -->
<!-- ggplot(results_train, aes(x = HOUSING_STATUS)) + -->
<!--   geom_bar(stat = "count") -->
<!-- ``` -->

<!-- ## Years at Current Job -->

<!-- ```{r echo=FALSE} -->
<!-- ggplot(results_train, aes(x = YEARS_AT_CURRENT_JOB)) + -->
<!--   geom_histogram(binwidth = 2) -->
<!-- ``` -->

<!-- ## Employer Organization Type -->

<!-- ```{r echo=FALSE} -->
<!-- ggplot(results_train, aes(x = EMPLOYER_TYPE)) + -->
<!--   geom_bar(stat = "count") -->
<!-- ``` -->

<!-- ## Years Since Getting Current Identity Documnent -->

<!-- ```{r echo=FALSE} -->
<!-- ggplot(results_train, aes(x = YEARS_SINCE_GETTING_IDENTITY_DOCUMENT)) + -->
<!--   geom_histogram() -->
<!-- ``` -->

<!-- ## Rating of Region -->

<!-- ```{r echo=FALSE} -->
<!-- ggplot(results_train, aes(x = REGION_AND_CITY_RATING)) + -->
<!--   geom_bar(stat = "count") -->
<!-- ``` -->


